---
title: "buoy"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(stringr)
library(lubridate)

url_1 <- "http://www.ndbc.noaa.gov/view_text_file.php?filename=mlrf1h"
url_2 <- ".txt.gz&dir=data/historical/stdmet/"
years <- c(1999:2018)
urls <- str_c(url_1, years, url_2, sep = "")
filenames <- str_c("mr", years, sep = "")
#  Read the data from the website

# Year 1999 - 2006
for(i in 1:8){
  suppressMessages(
    assign(filenames[i], read.table(urls[i], header = TRUE, fill = TRUE))
  )
  
}
# Year 2007 - 2018
for(i in 9:20){
  suppressMessages(
    assign(filenames[i], read.table(urls[i], header = FALSE, fill = TRUE, col.names = colnames(mr2006))),
  )
  
}

mr1999$TIDE <- NA
n <- length(urls)
for (i in 1:n){
  file <- get(filenames[i])
  colnames(file)[1] <-"YYYY"
  if(ncol(file) == 18){
    file <- subset(file, select = -mm )
  }
  if(i == 1){
    MR <- file
  }else{
    MR <- rbind.data.frame(MR, file)
  }
  
}
#Assemble the data into a single data frame

MR$WVHT <- NA
MR$DPD <- NA
MR$APD <- NA
MR$MWD <- NA
MR$DEWP <- NA
MR$VIS <- NA
MR$TIDE <- NA
#Convert the null column to NA

MR$WD <- na_if(MR$WD,999)
MR$WSPD <- na_if(MR$WSPD,99)
MR$GST <- na_if(MR$GST,99)
MR$BAR <- na_if(MR$BAR,9999)
MR$ATMP <- na_if(MR$ATMP,999)
MR$WTMP <- na_if(MR$WTMP,999)
#Convert the null data to NA

MR_posix <- mutate(MR,data_time=ymd_h(str_c(YYYY,MM,DD,hh,sep = "/")))
View(MR_posix)
#Transform the date-time data into posix numbers

hh0 <- filter(MR_posix,hh==0)
View(hh0)
library(rstanarm)

fit_1 <- stan_glm(hh0$ATMP~hh0$YYYY,data=hh0)
plot(hh0$YYYY,hh0$ATMP,main = "1999-2018 Air Temperature at 0 o' clock",xlab = "Years",ylab = "Air Temperature",pch=20)
a_0 <- coef(fit_1)[1]
b_0 <- coef(fit_1)[2]
abline(a_0,b_0)
#1999-2018 Air temperature at 0 o' clock 
  
n <- 1
x <- c(1999:2018)
y <- c()
for (i in 1999:2018)
{
  y[n] <- c((mean(MR$ATMP[MR$YYYY==i],na.rm = T)))
   n <- n+1
}
ave1 <- data.frame(x,y)
fit_2 <- stan_glm(y~x,data = ave1)
plot(x,y,main="1999-2018 Average Air Temperature ",xlab = "Years",ylab = "Air Temperature",pch=20)
a_1 <- coef(fit_2)[1]
b_1 <- coef(fit_2)[2]
abline(a_1,b_1)
#1999-2018 Average Air Temperature

hh1 <- filter(MR_posix,hh==1)
View(hh1)

fit_3 <- stan_glm(hh1$WTMP~hh1$YYYY,data=hh1)
plot(hh1$YYYY,hh1$WTMP,main = "1999-2018 Water Temperature at 1 o' clock",xlab = "Years",ylab = "Water Temperature",pch=20)
a_2 <- coef(fit_3)[1]
b_2 <- coef(fit_3)[2]
abline(a_2,b_2)
#1999-2018 Water Temperature at 1 o' clock

m <- 1
x_1 <- c(1999:2018)
y_1 <- c()
for (i in 1999:2018)
{
  y_1[m] <- c((mean(MR$WTMP[MR$YYYY==i],na.rm = T)))
  m <- m+1
}
ave2 <- data.frame(x_1,y_1)
fit_4 <- stan_glm(y_1~x_1,data = ave2)
plot(x,y,main="1999-2018 Average Water Temperature ",xlab = "Years",ylab = "Water Temperature",pch=20)
a_3 <- coef(fit_4)[1]
b_3 <- coef(fit_4)[2]
abline(a_3,b_3)
#1999-2018 Average Water Temperature
```


My report:

1.My understanding of the question:
The question can be divided into four parts:
Firstly, I need to collect the data from NDBC Station. According to the task, 20-years of data is needed. Therefore, assembling these data into a single data frame is indispensable.Treating these data as a whole to analyze is what the task requires. Here the question comes: how can I input these tons of data as a single data set?
Secondly, null data is inevitable. Find the data unused and make substitutions. Besides, these NA data cannot be used in the later regression.
Thirdly, transform the date-time data into posix numbers. The data-time data is just a bunch of meaningless numbers, which cannot be identified as a time variable. So we need to make a transformation to deal with it.
Finally, make an analysis from these data. In this part, regression models are necessary.

2.My approach:
Some useful R packages make sense to these questions."Tidyverse","stringr","lubridate" and "rstanarm" are effective in solving these problems. Through these packages, the problem can be solved without much effort.

3.How I organize my work and make conclusions?
By querying a lot of information about R packages, I learned how to use them for data import and data processing. Starting from the four parts of the question, each part needs to be solved in a specific way. According to the different problems, find the appropriate R package, find the relevant function and use the function to try to solve the problem. That's how I organize my work.
My conclusion: Large amounts of data collected showed that water temperature and air temperature are in the form of a rising trend year by year.According to common sense, this trend is reasonable because of the global warming phenomenon. I make the conclusion by the reason that the regression model shows the coefficient is positive, which means the slope of the fit line is positive. 